Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-26 inst/examples/20170201-manuscript.Rmd
ok

```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}
df <- df0
catal <- "Kungliga"
df <- df %>%
        filter(catalog == catal) %>%
	#filter(country == "Finland" | publication_place == "Vyborg") %>%
        filter(publication_year >= 1640 & publication_year <= 1828)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs,
           labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle("Figure 9")       
       #ggtitl(paste("Publishers (", catal, ")", sep = ""))

>>>>

```{r Fig9, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=12}

df <- df0
catal <- "Kungliga"
df <- df %>%
        filter(catalog == catal) %>%
	#filter(country == "Finland" | publication_place == "Vyborg") %>%
        filter(publication_year >= 1640 & publication_year <= 1828)

@@

# Order by total publishing activity
npub$publication_place <- as.character((npub$publication_place))

npub <- npub %>% group_by(publication_decade, publication_place) %>%
                       summarise(n = sum(n))

levs <- npub %>%
  group_by(publication_place) %>%				             
  summarise(total = sum(n)) %>%					     
  arrange(desc(total))
levs <- levs$publication_place

npub$publication_place <- factor(npub$publication_place, levs)
npub <- npub %>% arrange(publication_place)
npub$publication_place <- factor(npub$publication_place,
                                 levels = rev(unique(npub$publication_place)))

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs,
           labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle("Figure 9")

print(p)
